MISUSES AND INACCURACIES OF PAGEL'S LAMBDA ML ESTIMATION METHODS

### 2020-03-15 Manuscript-template.rmd
kint attempt - success
moved rench's rule docs into Example folder

rmd files in main folder are to be edited for lambda manuscript

---
# A multivariate equivalency and general test for Rensch's Rule: Implications for the evolution of sexual shape dimorphism

@@

**Keywords**: Sexual dimorphism, multivariate, morphological evolution \hfill\break

**Short Title**: Multivariate Test of Rensch's Rule \hfill\break

>>>>

---
# Misuses and Inaccuracies of Pagel's Lambda ML Estimation Methods

@@

**Keywords**: Pagel's lambda, phylogenetic signal \hfill\break

**Short Title**: Problems with Pagel's lambda \hfill\break
